---
title: "initial_work_JC"
author: "Jenny Conde"
output: pdf_document
---

```{r libraries, include=FALSE, warning = FALSE}
library(data.table)
library(tidyverse)
library(janitor)
library(ggplot2)
library(dplyr)
library(patchwork)
library(tidyverse)
library(lmtest)
library(stargazer)
library(sandwich)
```

# Load Data and Explore with Summary

```{r load data, include = FALSE, warning = FALSE}
d <- fread('../W241_Survey_Results_Clean.csv')
```

```{r}
summary(d)
```


## Key Takeaways from Summary

* All responses were complete (`progress` only equals 100, and `finished` only equals TRUE)
* Need to convert some variables to factor variables (`how_old_are_you`, `what_is_your_gender`, `education_highest`, `familiar_with_test`, `taken_test_before`)
* Some people took forever to finish the survey --> we should probably filter our data to those who responded in <= 15 minutes (approx 1,000 seconds)

## Proportion Tables 

```{r}
prop.table(xtabs(~ what_is_your_gender, data = d))[1]
prop.table(xtabs(~ how_old_are_you, data = d))
prop.table(xtabs(~ education_highest + how_old_are_you, data = d))
prop.table(xtabs(~ familiar_with_test, data = d))
prop.table(xtabs(~ taken_test_before, data = d))
(xtabs(~ familiar_with_test + taken_test_before, data = d))
```

## Modifying Covariates

### Ideas of individuals to drop:
* Those who took >15 minutes (1,000 seconds) to complete the survey
* Those who responded not familiar with test but took test before

### Add new columns for compliers and treatment

```{r define vars for who received treatment and who complied}
d[, complier := ifelse(((d[, dob_day] %% 2 == 1) & (d[, compliance_q_glass] == 'Confetti (colored)')) | 
                         ((d[, dob_day] %% 2 == 0) & (d[, compliance_q_mclaughlin] == 'Fish')), TRUE, FALSE)]
d[, treatment := ifelse(d[, dob_day] %% 2 == 0, 'treatment', 'control')]
```

## Covariate Graphs

Notes

* There is a gender imbalance, but I think this is not a concern since men and women have relatively similar personality traits across both treatment and control
* The treatment group had more non-compliers than the control group. Perhaps this is because our treatment video was emotional and potentially triggering to some.
* Treatment group is smaller overall -- could be helpful to compare percentages across treatment and control groups for covariate balance checks rather than raw numbers

```{r, warning = FALSE}
d %>% ggplot(aes(x = duration_in_seconds)) + 
  geom_histogram() + theme_minimal() +
  labs(title = 'Time to Complete Survey',
       x = 'time (sec)') | 
  
  d[d[, duration_in_seconds] < 1000] %>% 
  ggplot(aes(x = duration_in_seconds)) + geom_histogram() + 
  labs(title = 'Time to Complete Survey (Filtered)',
       x = 'time (sec)') + 
  theme_minimal()
```

```{r hhi histogram, warning = FALSE}
d %>% filter(
  hhi >= 0
) %>% ggplot(aes(x = hhi)) + geom_histogram() + theme_minimal() +
  labs(title = 'Survey respondents skewed towards lower income families',
       x = 'household income factor variable')
```


```{r}
d %>% ggplot(aes(x = treatment)) + geom_bar() +
  theme_minimal() +
  labs(title = 'Treatment vs Control Distribution') +
  geom_text(aes(label = ..count..), stat = "count", vjust = -0.2)
```


```{r}
d %>% ggplot(aes(x = complier, fill = treatment)) + geom_bar(position = 'dodge') +
  theme_minimal() +
  labs(title = 'Compliers in Treatment and Control Groups')
```


```{r plot dist of personality types, warning = FALSE}
((d %>% ggplot(aes(x = personality_a)) + geom_histogram() + theme_minimal()) |
  (d %>% ggplot(aes(x = personality_c)) + geom_histogram() + theme_minimal()) |
  (d %>% ggplot(aes(x = personality_e)) + geom_histogram() + theme_minimal())) / 
  (d %>% ggplot(aes(x = personality_n)) + geom_histogram() + theme_minimal() |
     (d %>% ggplot(aes(x = personality_o)) + geom_histogram() + theme_minimal()))
```

```{r}
d %>% ggplot(aes(x = what_is_your_gender, fill = treatment)) + geom_bar(position = 'dodge') +
  theme_minimal() +
  labs(title = 'Gender distribution in treatment and control groups',
       x = 'Gender',
       fill = "Assignment")
```

```{r, warning = FALSE}
means <- d[treatment == 'control', .(mean(personality_a)), keyby = what_is_your_gender]
d %>% filter(
  treatment != 'control'
) %>% ggplot(aes(x = personality_a, color = what_is_your_gender)) + 
  geom_density() + 
  theme_minimal() +
  geom_vline(data = means, aes(xintercept = means$V1, color = what_is_your_gender),
             linetype = "dashed") + 
  labs(title = "Agreeableness distribution by gender",
       color = "Gender",
       x = "Agreeableness")
```

```{r, warning = FALSE}
means <- d[treatment == 'control', .(mean(personality_c)), keyby = what_is_your_gender]
d %>% filter(
  treatment != 'control'
) %>% ggplot(aes(x = personality_c, color = what_is_your_gender)) + 
  geom_density() + 
  theme_minimal() +
  geom_vline(data = means, aes(xintercept = means$V1, color = what_is_your_gender),
             linetype = "dashed") + 
  labs(title = "Conscientiousness distribution by gender",
       color = "Gender",
       x = "Conscientiousness")
```

```{r, warning = FALSE}
means <- d[treatment == 'control', .(mean(personality_e)), keyby = what_is_your_gender]
d %>% filter(
  treatment != 'control'
) %>% ggplot(aes(x = personality_e, color = what_is_your_gender)) + 
  geom_density() + 
  theme_minimal() +
  geom_vline(data = means, aes(xintercept = means$V1, color = what_is_your_gender),
             linetype = "dashed") + 
  labs(title = "Extraversion distribution by gender",
       color = "Gender",
       x = "Extraversion")
```

```{r, warning = FALSE}
means <- d[treatment == 'control', .(mean(personality_n)), keyby = what_is_your_gender]
d %>% filter(
  treatment != 'control'
) %>% ggplot(aes(x = personality_n, color = what_is_your_gender)) + 
  geom_density() + 
  theme_minimal() +
  geom_vline(data = means, aes(xintercept = means$V1, color = what_is_your_gender),
             linetype = "dashed") + 
  labs(title = "Neuroticism distribution by gender",
       legend = "Gender",
       x = "Neuroticism")
```

```{r, warning = FALSE}
means <- d[treatment == 'control', .(mean(personality_o)), keyby = what_is_your_gender]
d %>% filter(
  treatment != 'control'
) %>% ggplot(aes(x = personality_o, color = what_is_your_gender)) + 
  geom_density() + 
  theme_minimal() +
  geom_vline(data = means, aes(xintercept = means$V1, color = what_is_your_gender),
             linetype = "dashed") + 
  labs(title = "Openness distribution by gender",
       color = "Gender",
       x = "Openness")
```

```{r educ dist}
d %>% ggplot(aes(x = education_highest)) + geom_bar() + theme_minimal()
```

```{r}
d %>% ggplot(aes(x = familiar_with_test, fill = treatment)) + 
  geom_bar(position = 'dodge') + 
  ylim(0, 230) +
  theme_minimal() +
  labs(x = "Familiar with Test") +
  theme(legend.position = "none") |
  d %>% ggplot(aes(x = taken_test_before, fill = treatment)) + 
  geom_bar(position = 'dodge') + 
  ylim(0, 230) +
  theme_minimal() +
  labs(x = "Taken Test Before") +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank())
```


# Start Modeling



```{r}
compliers_only <- d %>% filter(
  complier == TRUE
)
coeftest(compliers_only[, lm(personality_e ~ treatment)])[1:2, ]
coeftest(compliers_only[, lm(personality_a ~ treatment)])[1:2, ]
coeftest(compliers_only[, lm(personality_c ~ treatment)])[1:2, ]
coeftest(compliers_only[, lm(personality_n ~ treatment)])[1:2, ]
coeftest(compliers_only[, lm(personality_o ~ treatment)])[1:2, ]
```

```{r}
filtered_d <- d %>% filter(
  complier == TRUE,
  duration_in_seconds <= 1000,
  !(taken_test_before == 'Yes' & familiar_with_test == 'No')
)
```


```{r}
coeftest(filtered_d[, lm(personality_e ~ treatment + how_old_are_you + 
                               what_is_your_gender + education_highest + 
                               familiar_with_test + taken_test_before)])[1:2, ]
coeftest(filtered_d[, lm(personality_a ~ treatment + how_old_are_you + 
                               what_is_your_gender + education_highest + 
                               familiar_with_test + taken_test_before)])[1:2, ]
coeftest(filtered_d[, lm(personality_c ~ treatment + how_old_are_you + 
                               what_is_your_gender + education_highest + 
                               familiar_with_test + taken_test_before)])[1:2, ]
coeftest(filtered_d[, lm(personality_n ~ treatment + how_old_are_you + 
                               what_is_your_gender + education_highest + 
                               familiar_with_test + taken_test_before)])[1:2, ]
coeftest(filtered_d[, lm(personality_o ~ treatment + how_old_are_you + 
                               what_is_your_gender + education_highest + 
                               familiar_with_test + taken_test_before)])[1:2, ]
```


```{r}
coeftest(filtered_d[, lm(personality_e ~ treatment + how_old_are_you + 
                           what_is_your_gender + education_highest + 
                           familiar_with_test + taken_test_before +
                           as.factor(ethnicity) + as.factor(hispanic) +
                           as.factor(political_party) + as.factor(region))])[1:2, ]
coeftest(filtered_d[, lm(personality_a ~ treatment + how_old_are_you + 
                           what_is_your_gender + education_highest + 
                           familiar_with_test + taken_test_before +
                           as.factor(ethnicity) + as.factor(hispanic) +
                           as.factor(political_party) + as.factor(region))])[1:2, ]
coeftest(filtered_d[, lm(personality_c ~ treatment + how_old_are_you + 
                           what_is_your_gender + education_highest + 
                           familiar_with_test + taken_test_before +
                           as.factor(ethnicity) + as.factor(hispanic) +
                           as.factor(political_party) + as.factor(region))])[1:2, ]
coeftest(filtered_d[, lm(personality_n ~ treatment + how_old_are_you + 
                           what_is_your_gender + education_highest + 
                           familiar_with_test + taken_test_before +
                           as.factor(ethnicity) + as.factor(hispanic) +
                           as.factor(political_party) + as.factor(region))])[1:2, ]
coeftest(filtered_d[, lm(personality_o ~ treatment + how_old_are_you + 
                           what_is_your_gender + education_highest + 
                           familiar_with_test + taken_test_before +
                           as.factor(ethnicity) + as.factor(hispanic) +
                           as.factor(political_party) + as.factor(region))])[1:2, ]
```

```{r}
filtered_d <- d %>% filter(
  # complier == TRUE,
  duration_in_seconds <= 1000,
  !(taken_test_before == 'Yes' & familiar_with_test == 'No')
)

filtered_compliers <- filtered_d %>% filter(
  complier == TRUE
)
```

```{r print model results function, echo = FALSE, warning = FALSE, results = 'asis'}
print_model_results <- function(personality_trait) {
  personality_trait <- toupper(personality_trait)
  if (personality_trait == 'A' | grepl("AGREE", personality_trait)) {
    personality_trait = "Agreeableness"
    
    itt_mod_simple <- filtered_d[, lm(personality_a ~ treatment)]
    itt_mod_covar <- filtered_d[, lm(personality_a ~ treatment + how_old_are_you + 
                             what_is_your_gender + education_highest + 
                             familiar_with_test + taken_test_before +
                             as.factor(ethnicity) +
                             as.factor(political_party) + as.factor(region))]
    cace_mod_simple <- filtered_compliers[, lm(personality_a ~ treatment)]   
    cace_mod_covar <- filtered_compliers[, lm(personality_a ~ treatment + 
                                                how_old_are_you + 
                             what_is_your_gender + education_highest + 
                             familiar_with_test + taken_test_before +
                             as.factor(ethnicity) +
                             as.factor(political_party) + as.factor(region))]
    
  } else if (personality_trait == 'C' | grepl("CON", personality_trait)) {
    personality_trait = "Conscientiousness"
    
    itt_mod_simple <- filtered_d[, lm(personality_c ~ treatment)]
    itt_mod_covar <- filtered_d[, lm(personality_c ~ treatment + how_old_are_you + 
                             what_is_your_gender + education_highest + 
                             familiar_with_test + taken_test_before +
                             as.factor(ethnicity) +
                             as.factor(political_party) + as.factor(region))]
    cace_mod_simple <- filtered_compliers[, lm(personality_c ~ treatment)]   
    cace_mod_covar <- filtered_compliers[, lm(personality_c ~ treatment + 
                                                how_old_are_you + 
                             what_is_your_gender + education_highest + 
                             familiar_with_test + taken_test_before +
                             as.factor(ethnicity) +
                             as.factor(political_party) + as.factor(region))]
    
  } else if (personality_trait == 'E' | grepl("EXTRA", personality_trait)) {
    personality_trait = "Extraversion"
    itt_mod_simple <- filtered_d[, lm(personality_e ~ treatment)]
    itt_mod_covar <- filtered_d[, lm(personality_e ~ treatment + how_old_are_you + 
                             what_is_your_gender + education_highest + 
                             familiar_with_test + taken_test_before +
                             as.factor(ethnicity) +
                             as.factor(political_party) + as.factor(region))]
    cace_mod_simple <- filtered_compliers[, lm(personality_e ~ treatment)]   
    cace_mod_covar <- filtered_compliers[, lm(personality_e ~ treatment + 
                                                how_old_are_you + 
                             what_is_your_gender + education_highest + 
                             familiar_with_test + taken_test_before +
                             as.factor(ethnicity) +
                             as.factor(political_party) + as.factor(region))]
    
  } else if (personality_trait == 'N' | grepl("NEUR", personality_trait)) {
    personality_trait = "Neuroticism"
    
    itt_mod_simple <- filtered_d[, lm(personality_n ~ treatment)]
    itt_mod_covar <- filtered_d[, lm(personality_n ~ treatment + how_old_are_you + 
                             what_is_your_gender + education_highest + 
                             familiar_with_test + taken_test_before +
                             as.factor(ethnicity) +
                             as.factor(political_party) + as.factor(region))]
    cace_mod_simple <- filtered_compliers[, lm(personality_n ~ treatment)]   
    cace_mod_covar <- filtered_compliers[, lm(personality_n ~ treatment + 
                                                how_old_are_you + 
                             what_is_your_gender + education_highest + 
                             familiar_with_test + taken_test_before +
                             as.factor(ethnicity) +
                             as.factor(political_party) + as.factor(region))]
    
  } else if (personality_trait == 'O' | grepl("OPEN", personality_trait)) {
    personality_trait = "Openness"
    
    itt_mod_simple <- filtered_d[, lm(personality_o ~ treatment)]
    itt_mod_covar <- filtered_d[, lm(personality_o ~ treatment + how_old_are_you + 
                             what_is_your_gender + education_highest + 
                             familiar_with_test + taken_test_before +
                             as.factor(ethnicity) +
                             as.factor(political_party) + as.factor(region))]
    cace_mod_simple <- filtered_compliers[, lm(personality_o ~ treatment)]   
    cace_mod_covar <- filtered_compliers[, lm(personality_o ~ treatment + 
                                                how_old_are_you + 
                             what_is_your_gender + education_highest + 
                             familiar_with_test + taken_test_before +
                             as.factor(ethnicity) +
                             as.factor(political_party) + as.factor(region))]
    
  } else {
    return("INVALID PERSONALITY TYPE")
  }
  
  itt_mod_simple_se <- sqrt(diag(vcovHC(itt_mod_simple, type = "HC1")))
  itt_mod_covar_se <- sqrt(diag(vcovHC(itt_mod_covar, type = "HC1")))
  cace_mod_simple_se <- sqrt(diag(vcovHC(cace_mod_simple, type = "HC1")))
  cace_mod_covar_se <- sqrt(diag(vcovHC(cace_mod_covar, type = "HC1")))
  
  stargazer(itt_mod_simple, itt_mod_covar, cace_mod_simple, cace_mod_covar,
            type = 'latex', 
            se = list(itt_mod_simple_se, itt_mod_covar_se, 
                      cace_mod_simple_se, cace_mod_covar_se),
            omit = c("how_old_are_you", "what_is_your_gender",
                     "education_highest", "familiar_with_test", "taken_test_before",
                    "ethnicity", "political_party", "region"),
            add.lines = list(c("Fixed effects?", "No", "Yes", "No", "Yes"),
                             c("Treatment p value", 
                               signif(coeftest(itt_mod_simple)[2, 4], digits = 3),
                               signif(coeftest(itt_mod_covar)[2, 4], digits = 3), 
                               signif(coeftest(cace_mod_simple)[2, 4], digits = 3),
                               signif(coeftest(cace_mod_covar)[2, 4], digits = 3))),
            column.labels = c("ITT", "ITT", "ATET", "ATET"),
            covariate.labels = c("Treatment", "Constant"),
            dep.var.labels = personality_trait,
            omit.stat = c("f", "ser"),
            star.cutoffs = c(0.05, 0.01, 0.001),
            title = paste('Model Results for ', personality_trait),
            header = FALSE)
}
```


```{r, echo = FALSE, results = 'asis', warning = FALSE}
print_model_results("A")
print_model_results("C")
print_model_results("E")
print_model_results("N")
print_model_results("O")
```

```{r, echo = FALSE, results = 'asis', warning = FALSE}
print_all_mod_results <- function() {
  a_mod <- filtered_compliers[, lm(personality_a ~ treatment + 
                                                how_old_are_you + 
                             what_is_your_gender + education_highest + 
                             familiar_with_test + taken_test_before +
                             as.factor(ethnicity) +
                             as.factor(political_party) + as.factor(region))]
  a_se <- sqrt(diag(vcovHC(a_mod, type = "HC1")))
  
  c_mod <- filtered_compliers[, lm(personality_c ~ treatment + 
                                                how_old_are_you + 
                             what_is_your_gender + education_highest + 
                             familiar_with_test + taken_test_before +
                             as.factor(ethnicity) +
                             as.factor(political_party) + as.factor(region))]
  c_se <- sqrt(diag(vcovHC(c_mod, type = "HC1")))
  
  e_mod <- filtered_compliers[, lm(personality_e ~ treatment + 
                                                how_old_are_you + 
                             what_is_your_gender + education_highest + 
                             familiar_with_test + taken_test_before +
                             as.factor(ethnicity) +
                             as.factor(political_party) + as.factor(region))]
  e_se <- sqrt(diag(vcovHC(e_mod, type = "HC1")))
  
  n_mod <- filtered_compliers[, lm(personality_n ~ treatment + 
                                                how_old_are_you + 
                             what_is_your_gender + education_highest + 
                             familiar_with_test + taken_test_before +
                             as.factor(ethnicity) +
                             as.factor(political_party) + as.factor(region))]
  n_se <- sqrt(diag(vcovHC(n_mod, type = "HC1")))
  
  o_mod <- filtered_compliers[, lm(personality_o ~ treatment + 
                                                how_old_are_you + 
                             what_is_your_gender + education_highest + 
                             familiar_with_test + taken_test_before +
                             as.factor(ethnicity) +
                             as.factor(political_party) + as.factor(region))]
  o_se <- sqrt(diag(vcovHC(o_mod, type = "HC1")))
  
  stargazer(a_mod, c_mod, e_mod, n_mod, o_mod,
          type = 'latex', 
          se = list(a_se, c_se, e_se, n_se, o_se),
          omit = c("how_old_are_you", "what_is_your_gender",
                   "education_highest", "familiar_with_test", "taken_test_before",
                  "ethnicity", "political_party", "region"),
          add.lines = list(c("Fixed effects?", "Yes", "Yes", "Yes", "Yes", "Yes"),
                           c("Treatment p value", 
                             signif(coeftest(a_mod)[2, 4], digits = 3),
                             signif(coeftest(c_mod)[2, 4], digits = 3), 
                             signif(coeftest(e_mod)[2, 4], digits = 3),
                             signif(coeftest(n_mod)[2, 4], digits = 3),
                             signif(coeftest(o_mod)[2, 4], digits = 3))),
          dep.var.labels = c("Agreeableness", "Conscientiousness", "Extraversion", 
                            "Neuroticism", "Openness"),
          covariate.labels = c("Treatment", "Constant"),
          omit.stat = c("f", "ser"),
          star.cutoffs = c(0.05, 0.01, 0.001),
          title = paste('ATET Model Results for All Personality Factors'),
          header = FALSE)
}
```

```{r, results = 'asis', warning = FALSE, echo = FALSE}
print_all_mod_results()
```

